\documentclass[12pt,a4paper,titlepage]{report}
\usepackage[utf8x]{inputenc}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}

\setlength{\headheight}{15pt}
\addtolength{\textwidth}{2cm}
\addtolength{\hoffset}{-1cm}

\fancyhead[L]{Progress Report}
\fancyfoot[L]{\thepage}
\fancyfoot[R]{\today}
\renewcommand{\headrulewidth}{0pt} 

\usepackage[parfill]{parskip}
\begin{document}
\input{title_page.tex} % Add the title page

\begin{abstract}
Abstract goes here.
\end{abstract}

\tableofcontents
\pagebreak

And then just do \chapter{chapter name}
And if you need to split it up use \section{section name}

\appendix
\chapter{Appendix}

\end{document}


The body of the progress report must not exceed 3,000 words. This is about 10 A4 pages of standard-spaced text.

The progress report should provide:

An enhanced project description (development of the brief above)
A report on the background research and literature search
The proposed final design of the system or experiment
A justification for the approach
An account of the work to date
A plan of the remaining work
An estimate of any support required to complete the project
A Gantt chart showing the schedule of both completed and remaining work
The presentation of the progress report must conform with the Project Report Standards shown below.

For electronic submission it is necessary to submit 2 PDF files via the ECS Handin System.

the progress report in PDF format for the Archive.
shorter version of the progress report in PDF format for Plagiarism Checking.
Following this, one paper copy of the report and a copy of the electronic submission acknowledgement sheet are submitted to Zepler reception.

Note that early submission of the progress report may be appropriate if a case for significant facilities or financial support needs to be made.

The progress report contributes about 10% of the final assessment.

Failure to submit a progress report in the approved format by the deadline will result in its part of the project mark being subject to a 10% penalty per working day late. A progress report submitted more than 5 days late will result in the relevant part of the project mark being set to zero.